\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-16 article.tex
some wording

The small decay for the fluorescent calcium indicator implies a signal
variation during a long time interval. Firing event are represented by
strong variations in the neuron activity. Therefore we apply a hard-tresholding
filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the
threshold $\tau$ should be taken positive to keep only rising edges and non
close to zeros in order to only consider strong variations.

@@

% Considering the short delay for a communication between neurons, slow events
% can be neglected to retrieve direct relationships. The average time
% delay is indeed about $1ms$ or $2ms$ while the fluorescent signal time
% resolution is $20ms$. Let us also highlight that even if two neurons are
% spatially far from each other, the delay should not exceed one time step. Thus very low frequency event can be neglected.

% Connectivity information between two neurons may be retrieved from successive
% and slightly delayed burst events. Direct links
% between two neurons should have shorter delay between fluorescence
% peaks than undirected links. However, the fluorescence signal has a slow
% decay compare to its rise. Therefore, we filter those unrelevant information
% with a hard thresholding filter
% \begin{align}
% X^{\prime\prime\prime}_{t,i} &=
% {X^{\prime\prime}_{t,i}}^{0.9} \mathbb{1}(X^{\prime\prime}_{t,i} \geq \tau) \forall i
% \label{eq:hard-treshold-filter}
% \end{align}
% where $\tau \geq 0$ is a parameter of the hard-threshold filter and the $0.9$
% exponent reduce the difference between peaks values.

@@

% Then we apply on all remaining timesteps $T$ a non-linear filter based on the current activity of the systems in order to favor the association measure when a medium size set of neurons are firing together, while artificially
% reducing the association measure in case of extreme network activity,
% i.e. high when a network firing is happening and low when no neuron is
% active:

% \begin{equation}
% X^{\prime\prime\prime\prime}_{t,i} =
% \left\{
%   \begin{array}{l}
%     1  : r_t < 0\\
%     {(X^{\prime\prime\prime}_{t,i} + 1)^{(a_t^{-1} + 1)}}^{g(r_t)} : r_t \geq 0
%   \end{array}
% \right.
% \text{ with }
% \left\{
%   \begin{array}{ll}
%     a_t &= \sum_{i=1}^p X^{\prime\prime\prime}_{t,i} +
%                        \frac{1}{2} X^{\prime\prime\prime}_{t-1,i} \forall t \in T\\
%     r_t &= \frac{a_t}{\max_{l \in T}{a_l}} \\
%   \end{array}
% \right.
% \end{equation}
% where $g(x) = b_1 I(f_4 < x < f_5) + b_2  I(f_5 \leq x < f_6) +
% b_3 (I(x\leq f_4) + I(f_ 6 \leq x))$ is a piecewise continuous function of
% parameters $b_1, b_2, b_3, f_4, f_5, f_6$. The coefficient were tuned
% for each set $i\in\left\{1, 2, 3, 4\right\}$ of coefficient
% $\left(c_l^i\right)_{l=-3}^2$.

% Finally since there is a high correlation between neurons, we perform noise
% filtering through a principal component analysis. From the $p$ eigen vectors,
% we kept $80\%$ of the eigen vectors which have the largest eigen value. In the
% context of the challenge, this assumption was deduced from ground truth of
% provided networks.

>>>>

The small decay for the fluorescent calcium indicator implies a signal
variation during a long time interval. Firing event are represented by strong
variations in the neuron activity. Therefore we apply a hard-tresholding
filter $x^{t,d}_i = x^{t,d}_i \mathbb{1}(x^{t,d}_i \geq \tau)$ where the
threshold $\tau$ should be taken positive and non-close to zero to
respectivelty only keep rising edges and strong variations.

@@

@@
